### 2025-05-06 manuscript/manuscript.Rmd
repository name change in manuscript
Add CSU affiliation

author: 
  - name          : "Claudia Friess"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : ""
    email         : "elasmophile@gmail.com"
    role:         
  - name          : "Eric C. Anderson"
    affiliation   : "2"
    role:
  - name          : "Lisa E. Ailloud"
    affiliation   : "3"
    role:
  - name          : "David S. Portnoy"
    affiliation   : "4"
    role:
  - name          : "Susan K. Lowerre-Barbieri"
    affiliation   : "1,5"
    role:

affiliation:
  - id            : "1"
    institution   : "Florida Fish and Wildlife Research Institute, St. Petersburg, FL, USA"
  - id            : "2"
    institution   : "NOAA, National Marine Fisheries Service, Southwest Fisheries Science Center, Fisheries Ecology Division, Santa Cruz, CA, USA"
  - id            : "3"
    institution   : "NOAA, National Marine Fisheries Service, Southeast Fisheries Science Center, Charleston, SC, USA"
  - id            : "4"
    institution   : "Marine Genomics Laboratory, Texas A&M University, Corpus Christi, Corpus Christi, TX, USA"
  - id            : "5"
    institution   : "University of Florida, Fisheries and Aquatic Sciences, Gainesville, FL USA"

@@

All code associated with analysis is available on https://github.com/cfriess/gag_ckmr.

>>>>

author: 
  - name          : "Claudia Friess"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : ""
    email         : "elasmophile@gmail.com"
    role:         
  - name          : "Eric C. Anderson"
    affiliation   : "2,3"
    role:
  - name          : "Lisa E. Ailloud"
    affiliation   : "4"
    role:
  - name          : "David S. Portnoy"
    affiliation   : "5"
    role:
  - name          : "Susan K. Lowerre-Barbieri"
    affiliation   : "1,6"
    role:

affiliation:
  - id            : "1"
    institution   : "Florida Fish and Wildlife Research Institute, St. Petersburg, FL, USA"
  - id            : "2"
    institution   : "NOAA, National Marine Fisheries Service, Southwest Fisheries Science Center, Fisheries Ecology Division, Santa Cruz, CA, USA"
  - id            : "3"
    institution   : Deptartment of Biology, Colorado State University, Fort Collins, CO, USA
  - id            : "4"
    institution   : "NOAA, National Marine Fisheries Service, Southeast Fisheries Science Center, Charleston, SC, USA"
  - id            : "5"
    institution   : "Marine Genomics Laboratory, Texas A&M University, Corpus Christi, Corpus Christi, TX, USA"
  - id            : "6"
    institution   : "University of Florida, Fisheries and Aquatic Sciences, Gainesville, FL, USA"

@@

All code associated with analysis is available on https://github.com/cfriess/protoherm_ckmr.
